An Open Repository of Real-Time COVID-19 Indicators

### 2021-10-04 indicators/paper/paper.tex
Comment out last revisions paragraph

To reiterate a previous point, when training and validating forecast models that
use signals (on historical data), users will want to use data that was known
\textit{as of} the forecast date, not revised versions that only became
available much later. The COVIDcast API makes all historical versions available
and easily accessible for this purpose; and this feature plays a prominent role
in our own analysis of forecasting and hotspot prediction models appearing in a
companion paper \cite{McDonald:2021}. Revisions to forecast targets, such as
cases and deaths, also complicate the evaluation of forecast models: comparisons
of forecasts to the ground truth may shift when the ground truth is revised
weeks later. Only by systematically tracking revisions can this effect be
monitored.

>>>>

To reiterate a previous point, when training and validating forecast models that
use signals (on historical data), users will want to use data that was known
\textit{as of} the forecast date, not revised versions that only became
available much later. The COVIDcast API makes all historical versions available
and easily accessible for this purpose; and this feature plays a prominent role
in our own analysis of forecasting and hotspot prediction models appearing in a
companion paper \cite{McDonald:2021}.% Revisions to forecast targets, such as 
% cases and deaths, also complicate the evaluation of forecast models:
% comparisons of forecasts to the ground truth may shift when the ground truth
% is revised weeks later. Only by systematically tracking revisions can this
% effect be monitored.
